Mapping Microblog Posts to Encyclopedia Articles

### 2011-03-14 trunk/lids/twittersearchwrap/paper/paper.tex

\newcommand{\myremark}[2]{{\textbf{\marginpar{$\parallel$}(* \textit{#1:} #2 *)}}}

@@

The architecture of our proposed system is shown in Figure~\ref{fig:arch}. Upon receipt of a query four steps are performed. In the following we will illustrate these steps using the example of a search for the hash tag $\#ka$, a hashtag which is frequently used to describe posts related to the city of Karlsruhe, Germany.

@@

\begin{enumerate}
	\item In a first step, the most recent search results for the query are
	obtained.\newline In our example, calling the Wrapper with query $\#ka$ will
	return a document containing all most recent Twitter posts whose content matched the search string $\#ka$ and their meta information.

An example for a single retrieved post is the following: \begin{sloppypar}
''\texttt{Just
returned from a wonderful holiday in \#ka.
\url{http://www.karlsruhe.de/stadt/tourismus.en}
@KarlsruheTweets}'',\end{sloppypar} posted by Twitter user
\texttt{sample\_user\_12345}; geo coordinates and the date the message has been posted are furthermore known.

@@

In our example, the message contains a link to
\url{http://www.karlsruhe.de/stadt/tourismus.en}, the official homepage of the
tourist office of the city of Karlsruhe. Dereferencing this URL and grabbing the
text found at the link gives us the following text:
\begin{sloppypar}''\texttt{Karlsruhe, where paths converge - a legendary city in the sunny south-west of Germany, famed for its fan-shaped historic street plan, where margraves reigned in times past, and German joie de vivre reigns today.}''
\end{sloppypar}	
	\item In a third step entities matching the search result are retrieved. The
	content of the Twitter messages that matched the search query and, if available, the content of referenced websites is merged to a single input string and used as input for the annotation. The result of this step is a list of matching articles of the English Wikipedia.

In our example, the contents of all posts related to the search term '\#ka' are
merged with the retrieved external website content. Thus, the post obtained from
step 1 would be matched with the website content obtained in step 2 into a
single input stream: \begin{sloppypar}"\texttt{Just returned from a wonderful
holiday in \#ka. \url{http://www.karlsruhe.de/stadt/tourismus.en}
@KarlsruheTweets. Karlsruhe, where paths converge - a legendary city in the
sunny south-west of Germany, famed for its fan-shaped historic street plan, where margraves reigned in times past, and German joie de vivre reigns today.}"\end{sloppypar}This string is appended to the Twitter content and the external content of all other posts in the result.

In the example, we would expect to find entities which are related to Karlsruhe, like Karlsruhe, Germany or the Karlsruhe\_Institute\_of\_Technology.

	\item	Finally, an RDF document is generated representing the search results and the annotations.

	Continuing our example, the output RDF document should contain the following
	triples to reference the DBPedia mappings:
    \begin{enumerate}
      \item \texttt{\#ka rdfs:seeAlso http://dbpedia.org/resource/Karlsruhe.}
      \item \texttt{\#ka rdfs:seeAlso http://dbpedia.org/resource/Germany.}
      \item \texttt{\#ka rdfs:seeAlso\newline
      http://dbpedia.org/resource/Karlsruhe\_Institute\_of\_Technology.}
    \end{enumerate}

	The Twitter posts matching the search term \#ka are likewise all described in
	the output document. Here, the description for the initially given post
	abbreviated \texttt{m} results in the following
	triples:
	\begin{enumerate}
      \item \texttt{twitter:m foaf:page\newline
      ``http://twitter.com/sample\_user\_12345/statuses/1234567890.''}
      \item \texttt{twitter:m dc:date ``2011-02-23T12:00:00Z''.}
      \item \texttt{twitter:m geo:lat ``49.010239''.}
      \item \texttt{twitter:m geo:long ``8.411879''.}
      \item \texttt{twitter:m foaf:maker twitter:sample\_user\_12345}
      \item \texttt{twitter:m dc:description ``Just returned from a
      wonderful\newline holiday in
      \#ka.\url{http://www.karlsruhe.de/stadt/tourismus.en}\newline @KarlsruheTweets''.}
    \end{enumerate}
\end{enumerate}

@@

In the Twitter Search Wrapper\footnote{Available at \url{http://km.aifb.kit.edu/services/twittersearchwrap/}} we provide an implementation of our approach.

The implementation is based on a set of existing components: Twitter search results are obtained by using the Twitter search API\footnote{\url{http://dev.twitter.com/doc/get/search}}. The result is a feed containing the 100 most recently published Twitter messages, which are publicly visible and match the query, and their authors. The messages themselves are described by their content, publishing date, authors
and optionally a geographic location.

The optional step of dereferencing URLs which are posted in messages contained
in the result set can be triggered using the option \texttt{extern=true} in our
system. To keep the input size for the next steps manageable, we do not use the
whole content of the referenced sites but only the first 50 words. The content
retrieved from external websites is beautified for our purpose removing
HTML-tags and scripting elements using the CyberNeko Java HTML Parser
Library\footnote{\url{http://sourceforge.net/projects/nekohtml/}}.

The Wikifier \cite{key:wikifier} is used for obtaining content annotations. This tool takes a text as input and returns a set of Wikipedia entities which are relevant for the analyzed text.

The system generates and outputs an RDF document containing a
semantic description of the retrieved messages matching the search query for the
given query and references to the DBpedia articles that have been returned by the Wikifier. It describes
the result by means of the popular vocabularies FOAF \cite{key:foaf}, Dublin Core\footnote{\url{http://dublincore.org/documents/dcmi-terms/}}, the Basic Geo Vocabulary \cite{key:geo}. The annotations are added to the search result using \texttt{rdf:seeAlso} links to DBpedia entities \cite{key:dbpedia} which are obtained by a direct transformation of the Wikipedia entities' URLs. DBpedia has been chosen as these entities allow for a more coherent presentation of the content in the context of RDF.

The example twitter message given in the previous section is represented in
the output of the Twitter Search Wrapper as follows:\newline
\linebreak
\texttt{<rdf:Description
rdf:about="http://km.aifb.kit.edu/services/\newline
twitterwrap/statuses/show/1234567890\#id">\newline
	<foaf:page
	rdf:resource="http://twitter.com/sample\_user\_12345/\newline
	statuses/1234567890"/>\newline
	<dc:date>2011-02-23T12:00:00Z</dc:date>\newline <geo:lat>49.010239</geo:lat>\newline 
	<geo:long>8.411879</geo:long>\newline
	<foaf:maker
	rdf:resource="http://km.aifb.kit.edu/services/\newline
	twitterwrap/users/show?screen\_name=sample\_user\_12345\#id"/>\newline <dc:description>\newline
	Just returned from a wonderful holiday in \#ka.
	\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets\newline
	</dc:description>\newline
	</rdf:Description>\newline}
	\linebreak
Furthermore the mappings to DBpedia articles returned by the Wikifier
are represented in the output document. In the Twitter Search Wrapper the
representation is done the following way, again using the introductory
example from the previous section:\newline
\linebreak
	\texttt{<rdf:Description rdf:about=""/>}\newline
	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/Germany"/>}\newline
	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/\newline
	Karlsruhe\_Institute\_of\_Technology"/>}\newline
	\texttt{</rdf:Description>}\newline

@@

We have conducted the evaluation on two sets of queries: the first set are the trending topics worldwide and in Germany on Twitter retrieved on February 24th 17:20h (GMT) -- these topics are listed in Table \ref{tbl:terms}. Trending topics are chosen as they cover a variety of recently talked about topics which due to its recent nature may be of high interest for further processing.

\begin{table}[ht*]
\centering
\begin{tabular}{ l }
Trending Topics Worldwide  \\
\hline
\#goodlucknickj  \\
\#smalljoys \\
\#thingsthedevilinvented \\
Adam Wainwright  \\
CatchPetrovaFire \\
Gadafi  \\
Libia \\
Precious Minaj \\
Tommy John  \\
\end{tabular}
\begin{tabular}{l}
Trending Topics Germany \\
\hline
\#gaddafi \\
\#guttenberg  \\
\#libya  \\
Doktorarbeit \\
Gef\"{u}hl  \\
Lion  \\
MBP \\
Thunderbolt \\
Vorratsdatenspeicherung \\
\end{tabular}
\caption{Search terms}\label{tbl:terms}
\end{table}

The second query set consists of hash tags that are frequently used on Twitter. To obtain these, we have sampled the Twitter message feed using Twitter's Streaming API for one minute twice an hour from 2011-03-03 to 2011-03-06. The top-50 hashtags dervied from the aggregate sample are listed in Table \ref{tbl:hashtags}, count is the number of times we encountered them during the collection period.

@@

nowplaying & 144 & 17 & 0.4514 & 0.0251 & 0.0565 & 0.0198 & 0.0458 & 0.0212 \\

@@

fb & 105 & 1 & 1.1705 & 1.1826 & 0.1083 & 0.0933 & - & - \\

@@

news & 46 & 0 & 1.8696 & 0.1943 & 0.1024 & 0.0210 & - & -  \\
jobs & 45 & 0 & 1.3866 & 0.4198 & 0.1006 & 0.0192 & - & - \\
libya & 44 & 1 & 16.0309 & 117.2024 & 0.2701 & 0.0427 & - & - \\
followmejp & 44 & 0	& 1.5398 & 0.1255 & 0.0688 & 0.0410 & - & -\\

@@

sougofollow & 39 & 0 & 2.1010 & 0.1820 & 0.0720 & 0.0427 & - & - \\

@@

nicovideo & 35 & 0 & 51.0720 & 5521.3529 & 0.3604 & 0.1893 & - & - \\

@@

followme & 26 & 0 & 3.2194 & 0.4650 & 0.1209 & 0.0952 &	- &	- \\

@@

win & 20 & 0 & 4.2949 & 5.1856 & 0.0347 & 0.0221 & - & - \\
tweetmyjobs & 20 & 0 & 35.5697 & 1590.6997 & 0.3244 & 0.0621 & - & - \\
music & 20 & 1 & 4.4665 & 4.6392 & 0.0833 & 0.0196 & - & - \\
in & 20 & 3	& 8.2367 & 6.8944 & 0.0649 & 0.0236 & 0.0251 & 0.0206 \\

@@

fui & 18 & 48 & 11.5515 & 165.3850 & 0.4896 & 0.2447 & 0.4635 & 0.2448 \\
bot &      18 & 1 & 13.3533 &	8.2469 & 0.2708 & 0.1975 & - & -  \\
nemuritsuzuketeshinu & 17 & 48 & 314.1120 & 25053.5657 & 1.0000 & 0.0000 & 1.0000 & 0.0000 \\

@@

	The mean $aut(q)$ and the variance $autv(q)$ of the $aut(R_i)$ can be used to describe update properties for the result sets that are generated for a given query. E.g. if for a given query $aut(q)$ is high and $autv(q)$ is low, then the rate at which messages are published is stable at a quite low level.
%	\item The global stability $gs$ of the results shows how stable the whole set of entity terms for a query is. It is defined as: $$gs(q)=\frac{|\bigcap_{i=1}^{n}E_i|}{|\bigcup_{i=1}^{n}E_i|}$$
%	A value of $gs(q)$ of $1$ means that the set of entities is the same at each point in time $t_i$. On the other hand, a value of $0$ means that at least two of the sets of entities, with which the results were annotated, are disjoint.
	\item The stability for a single term is defined as the fraction of result sets for a query $q$ in which it occurs: 
$$sts(q,t)=\frac{|\{i|t\in E_i\}|}{n}$$
	If the value of $sts$ is $1$ the term occurs in all of the result sets for the query, if it is close to $0$ it occurs in few result sets.
	\item The time stability $ts$ for a query $q$ at time $t_i$ is the fraction of
	entities which are unchanged between the result set at $t_{i-1}$ and $t_i$: $$ts(q,t_i)=\begin{cases} 1 & i=1 \\
														\frac{|E_{i-1}\cap E_i|}{|E_{i-1}\cup E_i|} & i>1\end{cases}$$
	A value of $1$ means that the two sets of entities are identical, a value of $0$ means they are disjoint.

@@

An overview of the results we obtained for the frequently used hash tags is given in Table~\ref{tbl:hashtags}. In total, we have analysed 48 result sets for each of the query tags. However, in some cases, the analysis which includes the content of external web pages led to a timeout of the Wikifier. $N_{ext}$ gives the number of result sets which we could analyse when the external content is included. $E(aut)$ and $Var(aut)$ give the results for analysing the average update times of the result sets. A low $E(aut)$ means that updates are frequently posted, a high $E(aut)$ means that updates are rather infrequent. In the case of our analysis estimated update frequencies range from $0.45$ seconds to $314.11$ seconds, i.e. approximately $5$ minutes. In order to avoid any duplicates in the result sets, an average update time of less than $18$ seconds is needed. Note that this value is only an average and does not guarantee disjointness of the result sets, as high update frequencies in one result set may outweigh low update frequencies in other result sets. Thus, we have additionally analysed the variance of the $aut$s. A low variance means that the update intervals remain relatively stable over time, while a high variance indicates that messages using the hash tag were posted rather irregularly. In general, higher average update times are associated with a higher variance in the update times. In some cases however, the variance of the average update time is surprisingly low when the mean average update time is rather high: this is e.g. the case for the tags $\#bieberfact$, $\#quran$, $\#followfriday$. For these tags updates came at a relatively regular level.

We also report the average time stability over all time points as well as the variance for each hash tag. A high time stability indicates that more or less the same entities were used for annotation at all times. The high stability of $1$ was achieved for the tag $\#nemuritsuzuketeshinu$, because no entities could be associated with the results of this search. This can be explained as the tag is only used by Japanese twitter users in Japanese twitter messages. However, the Wikifier analyses the content of the results as being English text.
A similar problem was encountered when analysing the trending topics in Germany. We assumed that these topics would mostly be tweeted about in German and thus called the German version of the Wikifier when analysing the results. However, it turned out that although the topics were trending in Germany, the tags were also used in messages in other languages.

Surprisingly, the second highest stability value was reached with the tag $\#partiu$ which is mainly used in Spanish twitter messages. 
\myremark{Uta}{Liegt auch an nichtgefundenen Entitäten}

The third highest stability was achieved by the tag $\#tilltheworldends$ which refers to Britney Spears' newest single. Accordingly, the entities which were most frequently used for annotation are "Britney Spears" ($95.83\%$), "iTunes" ($68.75\%$), "itunes" ($62.5\%$), "Itunes" ($31.25\%$), "Madonna\_(entertainer)" ($16.6\%$). The values in brackets indicate the single term stabilities for each of the terms.
\myremark{Uta}{Weiß jemand, wie Madonna da reinkommt? Gibt es ne Erklärung für die unterschiedlichen Schreibweisen von iTunes? JA, liegt am Wikifier der keine normalisierten URIs zurückliefert}

Very low time stability was obtained for the tag $\#nowplaying$ which is used to tell which song one is currently listening to (a similarly low stability is obtained for the tag $\#np$ which is often used synonymously with $\#nowplaying$). As these messages contain all kinds of artist names and songs names. It is thus expected that the entities which are found vary between the result sets. In this case the most frequent entities were "iTunes" ($52.08\%$), "Michael Jackson" ($33.3\%$), "Lady Gaga" ($33.3\%$), "Lil Wayne" ($29.16\%$), "Katy Perry" ($22.92\%$).
%\myremark{Uta}{In der Evaluationstabelle sollte dann auf jeden Fall noch dabei stehen, wie viele Resultsets wir zu den einzelnen Queries haben}

The effect of considering external content in the annotation is beneficial in some cases, in others the effect was destabilizing. 
\myremark{Uta}{Meine Hypothese wäre, dass es in Fällen, wo auf sehr unterschiedliche Quellen verwiesen wird, destabilisierend wirkt, in Fällen wo auf die gleichen/ähnliche Seiten verwiesen wird, stabilisierend - habe aber keine Daten, um das zu überprüfen.}
\myremark{todo}{Hypothesis: high average update time leads to stable results}

\subsection{Discussion}

@@@highlight the remarkable outcomes
@@@what is did we learn from the results?

@@

@@@ not possible to map one hashtag to a single dbpedia concept: \#ka may be used for Karlsruhe or Ford Ka

@@@ tricky to deal with different languages - wikifier (or any nlp technique) is language dependent, but the trending topics may be commented on in a variety of languages

@@@ how to select external data (parse text from HTML, which part of web page to select - boilerplate stuff might spoil the results (reference blog cleansing paper

>>>>

\newcommand{\myremark}[2]{{\textbf{\marginpar{$\parallel$}(* \textit{#1:} #2 *)}}}
%\newcommand*\justify{%
%  \fontdimen2\font=0.4em% interword space
%  \fontdimen3\font=0.2em% interword stretch
%  \fontdimen4\font=0.1em% interword shrink
%  \fontdimen7\font=0.1em% extra space
%}

@@

The architecture of our proposed system is shown in Figure~\ref{fig:arch}. Upon
receipt of a query $q$ four steps are performed. In the following we will illustrate
these steps using the example of a search for the hash tag $\#Libya$, a hashtag
which is frequently used to describe posts related to the country of Libya.

@@

\begin{enumerate}
	\item In a first step, the most recent search results $R$ for the query are
	obtained.\newline In our example, calling the Wrapper with query $\#Libya$ will
	return a document containing all most recent Twitter posts whose content
	matched the search string $\#Libya$ and their meta information. 
	\newline
	An example\footnote{\url{http://twitter.com/SenJohnMcCain/statuses/46619460060196865}}
for a single retrieved post is the following:
\begin{verbatim}
"Arab League calls for no-fly zone in \#Libya 
http://t.co/ZsLNIWa"}}
\end{verbatim}
,posted by Twitter user \texttt{SenJohnMcCain}; geo coordinates\footnote{The original Twitter message posted by SenJohnMcCain was not geotagged} and the date the message has been posted are furthermore known.

@@

In our example, the message contains a link to
\url{http://t.co/ZsLNIWa}, which redirects to an article on the situation in
Libya published on \url{http://reuters.com}. Dereferencing this URL and grabbing
the text found at the link should return the following text:
\begin{verbatim}
"Arab League calls for Libya no-fly zone-state TV - CAIRO, 
March 12 (Reuters) - The Arab League on Saturday called on the
U.N. Security Council to impose a no-fly zone on Libya, 
Egyptian state television reported, a decision that would give
a regional seal of approval that NATO has said is needed for 
any military action."
\end{verbatim}
	\item In a third step entities matching the search result are retrieved. The
	content of the Twitter messages that matched the search query and, if available, the content of referenced websites is merged to a single input string and used as input for the annotation. The result of this step is a list of matching articles of the English Wikipedia.

In our example, the contents of all posts related to the search term '\#Libya'
are merged with the retrieved external website content. Thus, the post obtained from
step 1 would be matched with the website content obtained in step 2 into a
single input stream:
\begin{verbatim}"Arab League calls for no-fly zone in #Libya
Arab League calls for Libya no-fly zone-state TV - CAIRO, 
March 12 (Reuters) - The Arab League on Saturday called on the 
U.N. Security Council to impose a no-fly zone on Libya, 
Egyptian state television reported, a decision that would give
a regional seal of approval that NATO has said is needed for 
any military action."}
\end{verbatim}
This string is appended to the Twitter content and the external content of all other posts in the result.

In the example, we would expect to find entities which are related to Libya,
like Libya, Gaddafi or the Arab\_League.

	\item	Finally, an RDF document is generated representing the search results and
	the annotations. Continuing our example, the output RDF document should contain the following
	triples to reference the DBPedia mappings:
	\begin{verbatim}
	<http://km.aifb.kit.edu/services/twittersearchwrap/searchwrap
	?q=\%23lybia>
     rdfs:seeAlso <http://dbpedia.org/resource/Lybia> ,
        <http://dbpedia.org/resource/Gaddafi> ,
        <http://dbpedia.org/resource/Arab\_League> .
  \end{verbatim}
	The Twitter posts matching the search term \#Libya are likewise all described
	in the output document. The description for the post from our example 
	%abbreviated \texttt{m} 
	results in the following triples:
	\begin{verbatim}
	<http://km.aifb.kit.edu/services/twitterwrap/statuses/
	show/46619460060196865\#id> 
		foaf:page <http://twitter.com/SenJohnMcCain/statuses/
			46619460060196865>;
		dc:date "2011-03-12T17:12:00Z" ;\newline geo:lat "49.010239" ;
		geo:long "8.411879" ;
		foaf:maker <http://km.aifb.kit.edu/services/twitterwrap/users/
			show?screen\_name=SenJohnMcCain\#id> ;
		dc:description "Arab League calls for no-fly zone in \#Libya 
			http://\newline t.co/ZsLNIWa" . 
	\end{verbatim}

\end{enumerate}

@@

In the Twitter Search Wrapper\footnote{Online at \url{http://km.aifb.kit.edu/services/twittersearchwrap/}} we provide an implementation of our approach.

The implementation is based on a set of existing components: 
\begin{itemize}
\item Twitter search results are obtained by using the Twitter search API\footnote{\url{http://dev.twitter.com/doc/get/search}}, a RESTful API which delivers search results in JSON. The result is a feed containing the 100 most recently published Twitter messages, which are publicly visible and match the query, and their authors. The messages themselves are described by their content, publishing date, authors
and optionally a geographic location.

\item The optional step of dereferencing URLs which are posted in messages contained
in the result set can be triggered using the option \texttt{extern=true} in our
system. To keep the input size for the next steps manageable, we do not use the
whole content of the referenced sites but only the first 50 words. The content
retrieved from external websites is beautified for our purpose removing
HTML-tags and scripting elements using the CyberNeko Java HTML Parser
Library\footnote{\url{http://sourceforge.net/projects/nekohtml/}}.

\item The Wikifier \cite{key:wikifier} is used for obtaining content annotations. This tool takes a text as input and returns a set of Wikipedia entities which are relevant for the analyzed text. It represents a state-of-the-art annotation tool. It was chosen as it allows for finding entities not from some tool-specific knowledge base but from dbpedia, which is one of the most widely used data sources within the Linked Open Data cloud.

\item The system generates and outputs an RDF document in RDF/XML Syntax containing a
description of the retrieved messages matching the search query for the given query and references to the DBpedia articles that have been returned by the Wikifier. It describes
the result by means of the popular vocabularies FOAF \cite{key:foaf}, Dublin
Core\footnote{\url{http://dublincore.org/documents/dcmi-terms/}}, the Basic Geo
Vocabulary \cite{key:geo}. A single twitter message is described by its
individual page using \texttt{foaf:page} predicate. The date and time the
message has been posted is specified using \texttt{dc:date} predicate. The messages content
is annotated using \texttt{dc:description}, while the geographic location of the
message is indicated by \texttt{geo:lat} and \texttt{geo:long} predicates. The
creator of the Twitter message is referenced by \texttt{foaf:maker} predicate which points to a service that
uses RDF to describe information related to a Twitter user which has previously
been implemented here at the institute as the message creators URI.

\end{itemize}

The annotations are added to the search result using \texttt{rdf:seeAlso} links to DBpedia entities \cite{key:dbpedia} which are obtained by a direct transformation of the Wikipedia entities' URLs. DBpedia has been chosen as these entities allow for a more coherent presentation of the content in the context of RDF.

%The example twitter message given in the previous section is represented in
%the output of the Twitter Search Wrapper as follows:\newline
%\linebreak
%\texttt{<rdf:Description
%rdf:about="http://km.aifb.kit.edu/services/\newline
%twitterwrap/statuses/show/1234567890\#id">\newline
%	<foaf:page
%	rdf:resource="http://twitter.com/sample\_user\_12345/\newline
%	statuses/1234567890"/>\newline
%	<dc:date>2011-02-23T12:00:00Z</dc:date>\newline
%	<geo:lat>49.010239</geo:lat>\newline <geo:long>8.411879</geo:long>\newline
%	<foaf:maker
%	rdf:resource="http://km.aifb.kit.edu/services/\newline
%	twitterwrap/users/show?screen\_name=sample\_user\_12345\#id"/>\newline
%	<dc:description>\newline Just returned from a wonderful holiday in \#ka.
%	\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets\newline
%	</dc:description>\newline
%	</rdf:Description>\newline}
%	\linebreak
%Furthermore the mappings to DBpedia articles returned by the Wikifier
%are represented in the output document. In the Twitter Search Wrapper the
%representation is done the following way, again using the introductory
%example from the previous section:\newline
%\linebreak
%	\texttt{<rdf:Description rdf:about=""/>}\newline
%	\texttt{<rdfs:seeAlso
%	rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
%	\texttt{<rdfs:seeAlso
%	rdf:resource="http://dbpedia.org/resource/Germany"/>}\newline
%	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/\newline
%	Karlsruhe\_Institute\_of\_Technology"/>}\newline
%	\texttt{</rdf:Description>}\newline

@@

We have conducted experiments on a set of queries which were identified to be hash tags which are frequently used on Twitter.
To obtain these, we have sampled the Twitter message feed using Twitter's
Streaming API for one minute twice an hour from 2011-03-03 to 2011-03-06. The
top-50 hashtags dervied from the aggregate sample are listed in Table
\ref{tbl:hashtags}, count is the number of times we encountered them during the
collection period.

@@

nowplaying & 144 & 17 & \textbf{0.4514} & \textbf{0.0251} & 0.0565 & 0.0198 & 0.0458 & 0.0212 \\

@@

fb & 105 & 1 & 1.1705 & 1.1826 & 0.1083 & 0.0933 & -- & -- \\

@@

news & 46 & 0 & 1.8696 & 0.1943 & 0.1024 & 0.0210 & -- & --  \\
jobs & 45 & 0 & 1.3866 & 0.4198 & 0.1006 & 0.0192 & -- & -- \\
libya & 44 & 1 & 16.0309 & 117.2024 & 0.2701 & 0.0427 & -- & -- \\
followmejp & 44 & 0	& 1.5398 & 0.1255 & 0.0688 & 0.0410 & -- & --\\

@@

sougofollow & 39 & 0 & 2.1010 & 0.1820 & 0.0720 & 0.0427 & -- & -- \\

@@

nicovideo & 35 & 0 & 51.0720 & 5521.3529 & 0.3604 & 0.1893 & -- & -- \\

@@

followme & 26 & 0 & 3.2194 & 0.4650 & 0.1209 & 0.0952 &	-- &	-- \\

@@

win & 20 & 0 & 4.2949 & 5.1856 & \textbf{0.0347} & 0.0221 & -- & -- \\
tweetmyjobs & 20 & 0 & 35.5697 & 1590.6997 & 0.3244 & 0.0621 & -- & -- \\
music & 20 & 1 & 4.4665 & 4.6392 & 0.0833 & 0.0196 & -- & -- \\
in & 20 & 3	& 8.2367 & 6.8944 & 0.0649 & 0.0236 & \textbf{0.0251} & 0.0206 \\

@@

fui & 18 & 48 & 11.5515 & 165.3850 & 0.4896 & \textbf{0.2447} & 0.4635 & \textbf{0.2448} \\
bot &      18 & 1 & 13.3533 &	8.2469 & 0.2708 & 0.1975 & -- & --  \\
nemuritsuzuketeshinu & 17 & 48 & \textbf{314.1120} & \textbf{25053.5657} & \textbf{1.0000} & \textbf{0.0000} & \textbf{1.0000} & \textbf{0.0000} \\

@@

	The mean $aut(q)$ and the variance $autv(q)$ of the $aut(R_i)$ can be used to describe update properties for the result sets that are generated for a given query. E.g. if for a given query $aut(q)$ is high and $autv(q)$ is low, then the rate at which messages are published is stable at a quite low level.
%	\item The global stability $gs$ of the results shows how stable the whole set of entity terms for a query is. It is defined as: $$gs(q)=\frac{|\bigcap_{i=1}^{n}E_i|}{|\bigcup_{i=1}^{n}E_i|}$$
%	A value of $gs(q)$ of $1$ means that the set of entities is the same at each point in time $t_i$. On the other hand, a value of $0$ means that at least two of the sets of entities, with which the results were annotated, are disjoint.
	\item The stability for a single term is defined as the fraction of result sets for a query $q$ in which it occurs: 
$$sts(q,t)=\frac{|\{i|t\in E_i\}|}{n}$$
	If the value of $sts$ is $1$ the term occurs in all of the result sets for the query, if it is close to $0$ it occurs in few result sets.
	\item The time stability $ts$ for a query $q$ at time $t_i$ is the fraction of
	entities which are unchanged between the result set at $t_{i-1}$ and $t_i$: 
	$$ts(q,t_i)=\begin{cases} 1 & i=1 \\
														1 & E_{i-1}\cup E_i = \emptyset\\														
														\frac{|E_{i-1}\cap E_i|}{|E_{i-1}\cup E_i|} & i>1\end{cases}$$
	A value of $1$ means that the two sets of entities are identical, a value of $0$ means they are disjoint.

@@

An overview of the results we obtained for the frequently used hash tags is given in Table~\ref{tbl:hashtags}. The most frequent entities for some of the tags are listed in Table~\ref{tbl:entities}. In total, we have analysed 48 result sets for each of the query tags. However, in some cases, the analysis which includes the content of external web pages led to a timeout of the Wikifier. $N_{ext}$ gives the number of result sets which we could analyse when the external content is included. $E(aut)$ and $Var(aut)$ give the results for analysing the average update times of the result sets. A low $E(aut)$ means that updates are frequently posted, a high $E(aut)$ means that updates are rather infrequent. In the case of our analysis estimated update frequencies range from $0.45$ seconds to $314.11$ seconds, i.e. approximately $5$ minutes. In order to avoid any duplicates in the result sets, an average update time of less than $18$ seconds is needed. Note that update times below this value do not guarantee disjointness of the result sets, as the value is only an average, and high update frequencies in one result set may outweigh low update frequencies in other result sets. Thus, we have additionally analysed the variance of the $aut$s. A low variance means that the update intervals remain relatively stable over time, while a high variance indicates that messages using the hash tag were posted rather irregularly. In general, higher average update times are associated with a higher variance in the update times. In some cases however, the variance of the average update time is surprisingly low when the mean average update time is rather high: this is e.g. the case for the tags $\#bieberfact$, $\#quran$, $\#followfriday$. For these tags updates came at a relatively regular level.

\begin{table}[ht]
\centering
\begin{tabular}{l|l|l|l}
Tag & extern & $E$ & $sts$ \\%& $E_2$ & $sts(E_2)$ & $E_3$ & $sts(E_3)$ \\
\hline
$\#tilltheworldends$ & false & Britney Spears .9583 \\
& &  iTunes & .6875 \\
& &  itunes & .625 \\ 
$\#nowplaying$ & false & iTunes & .5208 \\
& & Michael Jackson & .333 \\
& & Lady Gaga & .333 \\
$\#nowplaying$ & true & YouTube & .8235 \\
& & Hip Hop Music & .6471 \\
& & The Notorious B.I.G. & .5883 \\
$\#np$ & false & Chris Brown\_(entertainer) & .5 \\
& & Usher & .3125 \\
& & Lil Wayne & .2917 \\
$\#np$ & true & Chris Brown\_(entertainer) & .5 \\
& & YouTube & .375 \\
& & Ne-Yo & .315 \\
$\#thataintwinning$ & false & Mozilla Firefox & .2291 \\
& & Twitter & .2291 \\
& & twitter & .1667 \\
$\#thataintwinning$ & true & twitter & .5208 \\
& & Twitter & .5 \\
& & Two and a half men & .125 \\
$\#blackpeoplemovies$ & false & Devil & .4791 \\
& & Tyler Perry & .2708 \\
& & Harry Potter & .2292 \\
$\#blackpeoplemovies$ & true & Amazon.com & 1 \\
& & YouTube & 1 \\
& & amazon.com & 1
\end{tabular}
\label{tbl:entities}
\caption{Most frequent entities and their single term stabilities}
\end{table}

We also report the average time stability over all time points as well as the variance for each hash tag. A high time stability indicates that more or less the same entities were used for annotation at all times. The highest stabilities were achieved for the tags $\#nemuritsuzuketeshinu$ and $\#partiu$, because no (resp. very few) entities could be associated with the results of this search. This can be explained as the tags are only used in Japanese resp. Spanish twitter messages. However, the Wikifier analyses the content of the results as being English text. A solution could be to search only for English messages, however, this is not possible as Twitter messages have no language tags and location attributes are no sufficient indicator for the language in which a user will write messages.

The third highest stability was achieved by the tag $\#tilltheworldends$ which refers to Britney Spears' newest single. The different URIs which are used for annotation are explained by the fact, that the Wikifier does not return normalized entities.

Very low time stability was obtained for the tag $\#nowplaying$ which is used to tell which song one is currently listening to (a similarly low stability is obtained for the tag $\#np$ which is often used synonymously with $\#nowplaying$). As these messages contain all kinds of artist names and songs names, it is thus expected that the entities which are found vary between the result sets.

The effect of considering external content in the annotation is beneficial in some cases, in others the effect was destabilizing. The highest decrease in stability was observed for the tag $\#thataintwinning$, the highest increase occured for the tag $\#blackpeoplemovies$. Our hypothesis is that destabilization occurs especially in cases where the posted links cover a variety of topics, while for more specific hash tags referenced web sites are more likely to cover a specific topics and will thus be stabilizing.

@@

We have presented an approach for annotating search results on microblogging platforms with Wikipedia entities. Our evaluation has shown that a direct mapping of hashtags to a single dbpedia concept is not possible in many cases. One reason is the use of hashtags in different contexts, another reason is that hash tags do not necessarily describe an entity, but are rather used to describe contexts.

Another difficult problem we encountered is that different languages have to be dealt with: Topics are often commented on in a variety of languages on microblogging platforms. However, NLP techniques which are used to analyze the messages are language dependent.

%@@@ how to select external data (parse text from HTML, which part of web page to select - boilerplate stuff might spoil the results (reference blog cleansing paper
